### 2021-05-03 manuscript.Rmd
implemented data.table, BFDA, modified Bayes + SPRT with sample sizes matched to OBF

```{r setup, include = FALSE}
knitr::opts_chunk$set()
library(papaja)
library(tidyverse)
library(ggplot2)
library(grid)
library(rpact)
library(pracma)
library(coda)
library(BayesFactor)
library(parallel)
library(metafor)
library(citr)
library(MSPRT)
library(TOSTER)

@@

Add writing on the modified SPRT.

@@

```{r include = F}
zz = gzfile("simulations/simulation001.csv.gz", 'rt')
df = read.csv(zz, header = T)

@@

t1 = df %>% filter(d_forpower == d_actual) %>%
  group_by(name) %>% 
  summarize(true_positive = mean(decision == "Reject") %>% round(2),
            inconclusive = mean(decision == "FTR") %>% round(2),
            false_negative = mean(decision == "SupportNull") %>% round(2))

t2 = df %>% filter(d_actual == 0) %>% 
  group_by(name) %>% 
  summarize(true_negative = mean(decision == "SupportNull") %>% round(2),
            inconclusive = mean(decision == "FTR") %>% round(2),
            false_positive = mean(decision == "Reject") %>% round(2))
```

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set()
library(papaja)
library(tidyverse)
library(ggplot2)
library(grid)
library(rpact)
library(pracma)
library(coda)
library(BayesFactor)
library(parallel)
library(metafor)
library(citr)
library(MSPRT)
library(TOSTER)
library(BFDA)

@@

Add writing on the modified SPRT. 
Add writing on the combination of fixed sample NHST and equivalence test.
Rewrite settings for O'Brien-Fleming: look after 50%, 75%, 100%.
Add writing on the implemented bias corrections for GS designs - median unbiased ES from rpact
Add writing on naive effect size estimate Bayes
Rephrase decision wording: refer to rejecting the null, rejecting the alternative, and inconclusive.
Change writing modified SBF prior from Stefan et al. 2020 - informed normal distribution centered on the population effect size (mean 0.5, variance 0.3).

Here's some examples on how SBFs are used in practice https://github.com/nicebread/BFDA/blob/master/BFDA_examples.md

@@

```{r include = F}
df = read.csv("simulations/simulation001.csv")
#zipped.df = gzfile("simulations/simulation001.csv.gz", 'rt')
#df = read.csv(zipped.df, header = T)

@@

t1 = df %>% filter(d_forpower == d_actual) %>%
  group_by(name) %>% 
  summarize(true_positive = mean(decision == "reject.null") %>% round(2),
            inconclusive = mean(decision == "inconclusive") %>% round(2),
            false_negative = mean(decision == "reject.alt") %>% round(2))

t2 = df %>% filter(d_actual == 0) %>% 
  group_by(name) %>% 
  summarize(true_negative = mean(decision == "reject.alt") %>% round(2),
            inconclusive = mean(decision == "inconclusive") %>% round(2),
            false_positive = mean(decision == "reject.null") %>% round(2))
```
